An HPSG account for verbal reduplication in Mandarin Chinese

### 2023-06-03 chapters/ch01-Intro.tex
Update 2023-06-03-19:08:01

In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning \citep[e.g.][]{Chao1968, LiThompson1981,  Li1996, Dai1997,  Zhu1998, Xing2000, Chen2001,  Tsao2001, Yang2003, XiaoMcEnery2004}. 
It means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
    in the example sentences will be set in italics.}
Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while”.

@@

The current study tries to determine a suitable formal and unified analysis for the structure of verbal reduplication in Mandarin Chinese.
It contributes more empirical evidence and 
offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG, \citealt{PollardSag1994}) to this phenomenon 
using Minimal Recursion Semantics (MRS, \citealt{Copestakeetal2005}) as the semantic representation formalism.
This new account avoids the problems of previous approaches and
explains more forms of verbal reduplication in Mandarin Chinese.

>>>>

In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning \citep[e.g.][]{Chao1968, LiThompson1981,  Li1996, Dai1997,  Zhu1998, Xing2000, Chen2001,  Tsao2001, Yang2003, XiaoMcEnery2004}. 
This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
    in the example sentences will be set in italics.}
Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while”.

@@

The current study tries to determine a suitable formal and unified analysis for the structure of verbal reduplication in Mandarin Chinese.
It contributes more empirical evidence and 
offers a novel analysis in the theoretical framework of Head-driven Phrase Structure Grammar (HPSG; \citealt{PollardSag1994, Sag1997, Mueller2013}) to this phenomenon 
using Minimal Recursion Semantics (MRS; \citealt{Copestakeetal2005}) as the semantic representation formalism.
This new account avoids the problems of previous approaches and
explains more forms of verbal reduplication in Mandarin Chinese.
